Wikipedia Text Mining and Entropy Analysis

### 2018-11-01 wiki_entropy/wiki_entropy.Rmd
normal approximation

LANGUAGE <- "Dutch" # This is the language you want to examine

system(paste("python3 get_wiki_df.py", LANGUAGE, sep = " "))
```

```{r slope_code, include = F, eval=F}
extract_wiki_tokens <- function(min_length, max_length, utterances) {

  tokens <- utterances %>% 
    mutate(gloss = str_trim(gloss)) %>%
    mutate(length = str_count(gloss, pattern = " +") + 1) %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n()) 
}

start_slope <- function(df) {

@@

@@

get_wiki_slopes <- function(min_length, max_length, utterances, REPS) {

>>>>

LANGUAGE <- "Alemannic" # This is the language you want to examine

system(paste("python get_wiki_df.py", LANGUAGE, sep = " "))
```

Extract tokens
```{r extract_tokens}
extract_wiki_tokens <- function(min_length, max_length, utterances) {

  tokens <- utterances %>% 
    mutate(gloss = str_trim(gloss)) %>%
    mutate(length = str_count(gloss, pattern = " +") + 1) %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n()) 
}
```

Slope helpers
```{r slope_helpers, include = F, eval=F}
start_slope <- function(df) {

@@

estimate_slope_normal <- function(df, first_pos, second_pos) {

   mutate(word_order = if_else(word_order == length-1, 2,
                                if_else(word_order == length -2, 1,
                                        0))) %>%

  df %>%
    ungroup() %>%
    filter(word_order >= first_pos, word_order <= second_pos) %>%
    mutate(word_order = word_order - max(word_order)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2")) %>%
    lm(entropy ~ length + I(length^2) + word_order, data  = .) %>%
    tidy() %>%
    filter(term == "word_order")

@@

}
```

```{r get_slopes}
get_wiki_slopes <- function(min_length, max_length, utterances, REPS) {
